Character LSTM for Sentiment Analysis on Twitter

### 2015-12-21 paper/paper.tex
added future work

As Table ~\ref{table:results} shows, \cite{kalchbrenner2014convolutional} outperform our character LSTM on the Go dataset. However, the results presented for our character and word-level models achieve competitive performance on the Go dataset without tuning hyperparameters such as learning rate and network width.

@@

Table ~\ref{table:word-sim} shows that related spellings or variants of a word are mapped to nearby points in the final encoding. The word encodings are obtained by feeding as input individual words (from the dataset vocabulary) to the character input LSTM model and obtaining the encoding of the words at the last layer (before the softmax).
We then find the closest neighbors of every word in this encoding space, where closeness is measured by cosine similarity. As desired, orthographic variations of the same word ``type'' are close together in the encoding space. In particular, it is worth noting that "woohoo" with different number of ``o'' are all close. Similarly, the word "sowwy" which is a common way of saying ``sorry" in such informal conversations is also close to the correct word.

@@

>>>>

As Table ~\ref{table:results} shows, word/dcnn \cite{kalchbrenner2014convolutional} outperform our character LSTM on the Go dataset. Note that this is the published result. The results presented for our character and word-level models achieve competitive performance on the Go dataset without tuning hyperparameters such as size of embeddings, number of hidden units and learning rate. We expect the results to improve after a thorough tuning of these parameters.

@@

Table x`~\ref{table:word-sim} shows that related spellings or variants of a word are mapped to nearby points in the final encoding. The word encodings are obtained by feeding as input individual words (from the dataset vocabulary) to the character input LSTM model and obtaining the encoding of the words at the last layer (before the softmax).
We then find the closest neighbors of every word in this encoding space, where closeness is measured by cosine similarity. As desired, orthographic variations of the same word ``type'' are close together in the encoding space. In particular, it is worth noting that "woohoo" with different number of ``o'' are all close. Similarly, the word "sowwy" which is a common way of saying ``sorry" in such informal conversations is also close to the correct word.

@@

Future work will explore other variants on the architecture presented in this paper, for example having explicit representation of words at the higher layers composed from the character encodings of the lower layer, inspired by the results of \cite{ling2015finding}. Empirical evidence, as well as intuition, suggests that the character-level models need to be {\it deep} in order to get reasonable performance. In this work we experimented with a two layer model and would like to try deeper models where Highway networks \cite{srivastava2015training} like connections between layers could help training. Another direction of research to get better sentiment analysis results could be to explore the addition of additional engineered features into the models.
